MINOS Handover Plots

### 2023-05-25 minos/validation/handovers.Rmd
Added spaghetti handovers for hh_income and SF_12 to handovers.Rmd

```{r}
source('Minos/minos/validation/utils.r')
```

@@

out.path <- 'Minos/output/default_config/'
base.dat <- read_output(out.path, 'baseline')
```

@@

#rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
#   raw.income.check, base.income.check)
```

@@

ggsave(filename = 'SF12_wav1.png',
       plot = last_plot(),
       path = save.path)
```

>>>>

```{r}
source('Minos/minos/utils_datain.R')
source('Minos/minos/utils_validation_vis.R')
```

@@

out.path <- 'Minos/output/default_config/'
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

@@

rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
   raw.income.check, base.income.check)
```

### Spaghetti

```{r}
raw.inc <- raw.dat %>%
  select(pidp, age, time, hh_income)
base.inc <- base.dat %>%
  select(pidp, age, time, hh_income)

income.spag <- rbind(raw.inc, base.inc)

spaghetti_plot(income.spag, 'hh_income',
               save = TRUE,
               save.path = save.path)

rm(raw.inc, base.inc, income.spag)
```

@@

ggsave(filename = 'SF12_wav1.png',
       plot = last_plot(),
       path = save.path)

rm(raw.sf12, base.sf12, sf12, raw.sf12.wave1, raw.sf12.2, base.sf12.2, sf12.2)
```

### Spaghetti

```{r}
raw.sf12 <- raw.dat %>%
  select(pidp, age, time, SF_12)
base.sf12 <- base.dat %>%
  select(pidp, age, time, SF_12)

sf12.spag <- rbind(raw.sf12, base.sf12)

spaghetti_plot(sf12.spag, 'SF_12',
               save = TRUE,
               save.path = save.path)

rm(raw.sf12, base.sf12, sf12.spag)
```
